fdcoexist

### 2018-08-20 paper_simulations.Rmd
Attempt of synthetic plot: weighted lm Rsquared between t2 and optim_env

@@

>>>>

## Synthetic plot

```{r synthetic_plot}

list_df <- list("no_compet_no_cor_df" = no_compet_no_cor_df,
                "no_compet_low_cor_df" = no_compet_low_cor_df,
                "no_compet_high_cor_df" = no_compet_high_cor_df,
                "compet_no_cor_df" = compet_no_cor_df,
                "compet_low_cor_df" = compet_low_cor_df,
                "compet_high_cor_df" = compet_high_cor_df)
list_df <- mapply(cbind, list_df, "df" = names(list_df), SIMPLIFY = FALSE)

all_df <- as.data.frame(bind_rows(list_df))

# List of weighted linear regressions
trait2_w_lm = all_df %>%
    group_by(df, scenario) %>%
    do(model = lm(trait2 ~ patch_optim, data = ., weights = N))

list_lm_df <- trait2_w_lm[[1]]
list_lm_scenario <- trait2_w_lm[[2]]

trait2_w_lm <- lapply(trait2_w_lm$model, summary)

synth_plot <- data.frame(df = list_lm_df,
                         scenario = list_lm_scenario,
                         r2 = unlist(lapply(trait2_w_lm,
                                            function(x) x$r.squared)))

synth_plot$df <- as.factor(synth_plot$df)
synth_plot$df <- factor(synth_plot$df,
                        levels(synth_plot$df)[c(6:1)])

print(ggplot(synth_plot, aes(as.factor(df), r2)) +
          geom_point(aes(shape = as.factor(scenario), fill = as.factor(scenario)),
                     color = "black", size = 4) +
          scale_fill_manual("Scenario", values = c(RA100100 = viridis::viridis(4)[1],
                                                   RA2575 = viridis::viridis(4)[2],
                                                   RA5050 = viridis::viridis(4)[3],
                                                   RA7525 = viridis::viridis(4)[4])) +
          scale_shape_manual("Scenario", values = c(RA100100 = 21, RA2575 = 22,
                                                    RA5050 = 23, RA7525 = 24)) +
          labs(subtitle = "R2 for the weighted linear regression between trait2 and environment",
               x = "Scenario",
               y = expression("R"^2)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)))

```

@@

## Synthetic plot

```{r synthetic_plot var_strength}

list_df <- list("no_compet_no_cor_df" = no_compet_no_cor_df,
                "no_compet_low_cor_df" = no_compet_low_cor_df,
                "no_compet_high_cor_df" = no_compet_high_cor_df,
                "compet_no_cor_df" = compet_no_cor_df,
                "compet_low_cor_df" = compet_low_cor_df,
                "compet_high_cor_df" = compet_high_cor_df)
list_df <- mapply(cbind, list_df, "df" = names(list_df), SIMPLIFY = FALSE)

all_df <- as.data.frame(bind_rows(list_df))

# List of weighted linear regressions
trait2_w_lm = all_df %>%
    group_by(df, scenario) %>%
    do(model = lm(trait2 ~ patch_optim, data = ., weights = N))

list_lm_df <- trait2_w_lm[[1]]
list_lm_scenario <- trait2_w_lm[[2]]

trait2_w_lm <- lapply(trait2_w_lm$model, summary)

synth_plot <- data.frame(df = list_lm_df,
                         scenario = list_lm_scenario,
                         r2 = unlist(lapply(trait2_w_lm,
                                            function(x) x$r.squared)))

synth_plot$df <- as.factor(synth_plot$df)
synth_plot$df <- factor(synth_plot$df,
                        levels(synth_plot$df)[c(6:1)])

print(ggplot(synth_plot, aes(as.factor(df), r2)) +
          geom_point(aes(shape = as.factor(scenario), fill = as.factor(scenario)),
                     color = "black", size = 4) +
          scale_fill_manual("Scenario", values = c(RA100100 = viridis::viridis(4)[1],
                                                   RA2575 = viridis::viridis(4)[2],
                                                   RA5050 = viridis::viridis(4)[3],
                                                   RA7525 = viridis::viridis(4)[4])) +
          scale_shape_manual("Scenario", values = c(RA100100 = 21, RA2575 = 22,
                                                    RA5050 = 23, RA7525 = 24)) +
          labs(subtitle = "R2 for the weighted linear regression between trait2 and environment",
               x = "Scenario",
               y = expression("R"^2)) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1)))

```
